
\subsection*{1.0}

There are 6 main issues we will focus on in economics:
\begin{itemize}
    \item \begin{definition}Productivity Growth\end{definition}
    Productivity is measured by ${Productivity=Output/Worker}$\\
    Incentives lead to productivity growth.
    \item \begin{definition} Population Growth\end{definition}
    Canada is open to immigrants, we have a low birth rate compared to past generations.
    No population growth leads to less workers, meaning workers must work harder.
    There are benefits and costs of having children.
    \item \begin{definition}Climate Change\end{definition}
    Cities in Canada and moving towards bodies of waters. Risk of submersion.
    Need to think about city design and allocation of people and resources.
    \begin{example}
        Farmers' harvests are affected by climate change. Impacts their income.
    \end{example}
    Economic impact of climate change is a big issue.
    \item \begin{definition}Technological Change\end{definition}
    Changing many industries, including education.
    Automation, job losses but also new job markets.
    Presently, might technological change may seem to be bad news but the future brings changes.
    \item \begin{definition}Protectionism\end{definition}
    Has been, unfortunately, on the rise over 20-40 years.
    Opposed to trade or comes with conditions.
    Countries have decided to tie trades to labour and climate conditions and standards.
    Free trade resists protectionism.
    \item \begin{definition}Inequality\end{definition}
    Highly undesirable, unless you are at the top of the distribution.
    Not within your control.
    Income inequality is problematic but has a deeper understanding. There is a difference between unfair and inequal.
    Need to analyze individual potential.
\end{itemize}